\documentclass[11pt, oneside]{article}   	
\usepackage{geometry} 
\usepackage{setspace}               		
\geometry{letterpaper}                   		
\usepackage[parfill]{parskip}    		
\usepackage{graphicx}					
\usepackage{amssymb}
\setlength{\parindent}{0em} 
\doublespacing




\title{Englisch}
\author{Elias Peeters}


\begin{document}
\maketitle

\pagebreak

\tableofcontents

\pagebreak

\section{Language}

\subsection{Nouns and adjectives with prepositions}

1. good at

2. dislike of/ for

3. experienced in/ at

4. fascinated by

5. characteristic of

6. information about/ on

7. interested in

8. knowledge about/ of

9. preference for

10. sign of

11. symbol of

12. typical of

13. view on/ about

\pagebreak

\subsection{Verbs and Adverbs}

1. agree to/ with/ on

2. comment on

3. complain about, of

4. consider (betrachten)

5. consist of

6. deal with 

7. decide on

8. describe

9. discuss

10. look at, for

11. refer to

12. suggest

13. think about, of

14. write about, for, to
\pagebreak

\subsection{Sentences for Nouns and Preposition}

1. I'm good at playing table tennis.

2. I'm fascinated by technic.

3. This sign gives information of the city..

4. I have knowledge about computers.

5. I'm interested in computers.

6. I'm experienced in climbing.

7. He has a preference for apples instead of pears.

8. Its typical for Mr. Weichel to come to late.



1. I comment on a video.

2. I have to deal with the problem.

3. I decided  to join the Physicsclass.

4. I suggest that we go home now.	

5. I think about many ideas when I sleep.

6. I never write letters to friends any more.

7. We discuss about the mobile usage in school.

8. He look for his mobile.

\pagebreak

\subsection{A dialog with false friends}

Two people are siting in cafe.

A: Hi Donald.

B: Hi Mark. 

A: How are you actual?

B: I'm fine, but a cafe would be perfect now.

A: Lets order a menu too.

B: I have little gift for you.

A: Please dont kill me.

\pagebreak

\section{Friends and Friendship}

I think there is not the friend. Everybody has lots of friends and the all are totaly different, but import for our personality. I, for example, have friends in my sport club. There are not my best friends, but it makes much fun to hang around with them. Also in school i have my friends. With many of my schoolmates I have a good amity too. But closly everybody on the world as one, two, or three best friends, who you talk to in a completely different way. Like the author A.A. Milne said once: "It is more fun to talk with someone who doesn't use long, difficult words but rather short, easy words like "What about lunch?"" A good friend is a person you can trust and who takes care of you and you of him. In my situation it looks a bit different at the first glance, but really same at the second.































\end{document}  